%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Sr Data Scientist} % Job title
{Enterprise Products} % Organization
{Houston, TX} % Location
{May 2019 - Current} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a recurrent neural net for predicting heat exchanger failures in the first 8 weeks. First model in production at Enterprise.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Data Scientist} % Job title
{Sanchez Energy} % Organization
{Houston, TX} % Location
{Apr 2017 - May 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a model fitting solution for determining a well's spontaneous (SP) log curve using peak detection methods and Kalman filters.
        The end result is used for identifying potential multi-million dollar fields to target.}
\item {Developed a Markov Chain Monte Carlo solution for simulating a well's decline curve and ultimate recovery.
        This solution is used to determine how much a well will make over it's lifetime before physically drilling it.}
\item {Optimized a geophysics simulator written in Python. Runtime went up by 6X and lines of code reduced by 10X.}
\item {Contributed to the development of a multi model prediction framework for predicting well production. 
        Framework is used to accurately predict a well's production and is used in planning and development of a field.}
\item {Contributed heavily to the development of automated methods for feature engineering, used in a number of projects.}
\item {Built and productionized a LSTM neural net for predicting a well's future flowback amount.}
\item {Developed operational alerts utilizing realtime data. Alerts include a deterministic model for detecting tubing leaks. 
        Annual cost savings is well over six figures.}
\item {Developed a multitude of data pipelines and workflows from a variety of sources (relational, non-relational, SCADA systems, etc).}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Data Analytics} % Job title
{Occidental Petroleum} % Organization
{Houston, TX} % Location
{Jan 2012 - Mar 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed and productionized a Monte Carlo simulation to determine the optimal number of workover rigs a field needs.}
\item {Built a logistic regression model for predicting the likelihood of IT tickets breaching their SLAs; achieved 87\% accuracy.}
\item {Implemented the first graph database (using neo4j) at Oxy for visualizing relationships between key data points. Visualization of 
        complex data flows simplified the understanding of how data moves throughout the organization's systems.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}